Download data

### 2024-02-28 scripts/subsetDataforCrews.Rmd
fn to write out when things peak flower

```{r generate projects for crews}

teams_list <- filter(teams, str_detect(Contract, 'SNDO|Eastern Mojave')) %>% 
  split(., f = .$Contract)

@@

tdf <- oppy[[1]] |>
  dplyr::arrange(taxon)

tdf <- dplyr::left_join(tdf, dates[[1]], by = 'doy')

dates <- date_maker()

>>>>

```{r}
teams_list <- filter(teams, str_detect(Contract, 'SNDO|Eastern Mojave')) %>% 
  split(., f = .$Contract)
```

```{r generate projects for crews, eval= F}

@@

tdf <- oppy[[1]] |>
  dplyr::arrange(taxon) |>
  dplyr::distinct()

dates <- date_maker()
tdf1 <- dplyr::left_join(tdf, dates[[1]], by = 'doy') |>
  dplyr::left_join(
    dplyr::select(dates[[2]], -doy), by = c('reports_to' = 'reporting_event')) |>
  dplyr::group_by(taxon) #|>
  tidyr::pivot_wider(names_from = reports_to, values_from = event, id_cols = 'taxon',
                     values_fill = NA)

report_pts_rep <- sort(as.numeric(colnames(tdf1)[grep('[0-9]', colnames(tdf1))]))
miss_wk <- setdiff(min(report_pts_rep):max(report_pts_rep), report_pts_rep) # see if some 
# weeks are missing by default. 
if(length(miss_wk)>0){

  empty_cols <- setNames(
    data.frame(
      matrix(
        NA, nrow = nrow(tdf1), ncol = length(miss_wk))), 
    miss_wk)

  tdf2 <- cbind(tdf1, empty_cols)
  rm(empty_cols)
}

tdf2 <- tdf2[, c(
  colnames(tdf2)[grep('[A-z]', colnames(tdf2))], 
  sort(as.numeric(colnames(tdf2)[ grep('[0-9]', colnames(tdf2)) ]))) ]

tdf2 <- tdf2[2:nrow(tdf2), ]

tdf_peak <- dplyr::filter(tdf, event == 'Peak') %>% 
  dplyr::mutate(
    Early_Peak = reports_to - 1, 
    Late_Peak = reports_to + 1 )
